A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-01 manuscript.Rmd
include hash in manuscript

@@

zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.

@@

<!-- public releases like preregistration, preprint -->
<!-- Hands on: add commit hash to results-->
<!-- Hands on: git tag + github release-->
<!-- Hands on: explain how to archive data-->
<!-- Hands on: explain how to archive docker images-->

>>>>

When you disseminate the paper across more locations than just GitHub it can be ambiguous which version of code and data have created the document (e.g. the manuscript.pdf).
To create a clear link between the repository version and some end result you can automatically include the hash of the commit.
Either you use Git from within R:

```{r}
system("git rev-parse --short HEAD")
```

Or you can use the `gert` package:

```{r}
strtrim(gert::git_commit_id(), 7)
```

@@

<!-- public releases like preregistration, preprint -->
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.

@@

<!-- Hands on: add commit hash to results-->
<!-- Hands on: git tag + github release-->
<!-- Hands on: explain how to archive data-->
<!-- Hands on: explain how to archive docker images-->
